---
title: "HW5"
author: "Chen Mo"
date: "11/16/2020"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1  

First, load the data.  
```{r}
homicide_data = 
        read_csv("./data/homicide-data.csv")
```
The raw data contains `r ncol(homicide_data)` columns and `r nrow(homicide_data)` rows in total. The data provides information of more than 52,000 criminal homicides over past decades in 50 of the largest American cities. The data includes the location of the killing, whether an arrest was made and, in most cases, basic demographic information about each victim.  

Then, clean the data.    
```{r}
homicide_df = 
        homicide_data %>%
        janitor::clean_names() %>% 
        mutate(
                city_state = str_c(city, state, sep = ", "),
                disposition = recode(disposition, "Closed without arrest" = "Unsolved"),
                disposition = recode(disposition, "Open/No arrest" = "Unsolved"),
                disposition = recode(disposition, "Closed by arrest" = "Solved")
        ) %>%
        select(city_state, disposition) %>% 
        filter(city_state != "Tulsa, AL")
```
Obtain the total number of homicides and the number of unsolved homicides.  
```{r}
homicide_total = 
        homicide_df %>% 
        group_by(city_state) %>% 
        summarise(
                hom_total = n(),
                hom_unsolved = sum(disposition == "Unsolved")
        )
```
Estimate the proportion of homicides that are unsolved in the city of Baltimore, MD.
```{r}
prop.test(
        homicide_total %>% filter(city_state == "Baltimore, MD") %>% pull(hom_unsolved),
        homicide_total %>% filter(city_state == "Baltimore, MD") %>% pull(hom_total)
) %>%
        broom::tidy() %>% 
        select(estimate, conf.low, conf.high)
```
Estimate the proportion of homicides that are unsolved in all cities.  
```{r}
results_df = 
        homicide_total %>% 
        mutate(
                prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
                tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
        ) %>% 
        select(-prop_tests) %>% 
        unnest(tidy_tests) %>% 
        select(city_state, estimate, conf.low, conf.high)
```
Creat a plot.  
```{r}
results_df %>% 
        mutate(
                city_state = fct_reorder(city_state, estimate)
        ) %>% 
        ggplot(aes(x = city_state, y = estimate)) +
        geom_point() +
        geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

# Problem 2  
Load the data and clean it.     
```{r}
path_df = 
        tibble(
                path = list.files("data/control and experimental")
        ) %>%
        separate(path, into = c("arm", "subject_ID", sep = 4)) %>% 
        mutate(
                arm = recode(arm, "con" = "control arm", "exp" = "experimental arm"),
                path = list.files("data/control and experimental"),
                path = str_c("./data/control and experimental/", path),
                data = map(.x = path, ~read_csv(.x))
        ) %>%
        select(arm, subject_ID, data) %>% 
        unnest(data) %>%
        pivot_longer(
                week_1:week_8,
                names_to = "week",
                values_to = "observations",
                names_prefix = "week_")
```

Make a spaghetti plot showing observations on each subject over time.
```{r}
path_df %>% 
        mutate(subject_ID = str_c(arm, subject_ID)) %>% 
        ggplot(aes(x = week, y = observations, color = arm, group = subject_ID)) +
        geom_point() +
        geom_line() + 
        labs(title = "Observations for each subjects over 8 weeks",
             subtitle = "Control arm VS Experimental arm",
             y = "Values of observations")
```
I also create a plot which shows values of observations by different arm on each subject over time.  
```{r}
path_df %>% 
        ggplot(aes(x = week, y = observations, color = subject_ID, group = subject_ID)) +
        geom_point(aes(shape = arm)) +
        geom_line() + 
        facet_grid(.~arm) +
        labs(title = "Observations for each subjects over 8 weeks",
             y = "Values of observations")
```
From the plots above, we can see that the values of observations of the experimental group have an increasing trend while the values of observations of the control group fluctuated a lot. The average value of observations of the experimental group is larger than that of observations of the control group.
# Problem 3  
